Semi-parametric generalized linear model for correlated binary data

### 2021-11-23 nuweb/SPGLM.tex
Protect against singular hessian
Complete C++ re-implementation of getTheta
Reuse precomputed hypergeometric probabilities in Hessian calculation

\begin{flushleft} \small\label{scrap1}\raggedright\small
\NWtarget{nuweb1}{} \verb@"../R/SPGLM.R"@\nobreak\ {\footnotesize {1}}$\equiv$
\vspace{-1ex}
\begin{list}{}{} \item
\mbox{}\verb@@\\
\mbox{}\verb@#' Fit semi-parametric GLM@\\
\mbox{}\verb@#'@\\
\mbox{}\verb@#'@{\tt @}\verb@rdname spglm@\\
\mbox{}\verb@#'@{\tt @}\verb@param formula a one-sided formula of the form \code{cbind(r, s) ~ predictors} where \code{r} and \code{s} give the number of responses and non-responses within each cluster, respectively (so the cluster size is \code{r+s}), and \code{predictors} describes the covariates.@\\
\mbox{}\verb@#'@{\tt @}\verb@param data  an optional matrix or data frame containing the variables in the formula \code{formula}. By default the variables are taken from \code{environment(formula).}@\\
\mbox{}\verb@#'@{\tt @}\verb@param subset  an optional vector specifying a subset of observations to be used.@\\
\mbox{}\verb@#'@{\tt @}\verb@param weights an optional vector specifying observation weights.@\\
\mbox{}\verb@#'@{\tt @}\verb@param offset  an optional vector specifying an offset term (predictor with a fixed coefficient of 1).@\\
\mbox{}\verb@#'@{\tt @}\verb@param link      a link function for the mean.@\\
\mbox{}\verb@#'@{\tt @}\verb@param mu0       an optional numeric value constraining the mean of the baseline distribution@\\
\mbox{}\verb@#'@{\tt @}\verb@param control a list with parameters controlling the algorithm.@\\
\mbox{}\verb@#'@{\tt @}\verb@return an object of class \code{spglm} with the fitted model.@\\
\mbox{}\verb@#'@{\tt @}\verb@export@\\
\mbox{}\verb@#' @{\tt @}\verb@importFrom stats terms model.matrix model.frame model.offset model.response model.weights@\\
\mbox{}\verb@@\\
\mbox{}\verb@spglm <- function(formula, data, subset, weights, offset, link="logit", mu0=NULL, @\\
\mbox{}\verb@                  control=list(eps=0.001, maxit=100)){@\\
\mbox{}\verb@@\\
\mbox{}\verb@    @\hbox{$\langle\,${\itshape Create model matrix from formula and data}\nobreak\ {\footnotesize \NWlink{nuweb2}{2}}$\,\rangle$}\verb@@\\
\mbox{}\verb@    @\\
\mbox{}\verb@    data_object <- list(model_matrix=mm, resp=Y, n=rowSums(Y), weights=weights, offset=offset, @\\
\mbox{}\verb@                        maxN=N, spt=0:N)@\\
\mbox{}\verb@    @\\
\mbox{}\verb@    @\hbox{$\langle\,${\itshape Fit model}\nobreak\ {\footnotesize \NWlink{nuweb7}{7}}$\,\rangle$}\verb@@\\
\mbox{}\verb@@\\
\mbox{}\verb@    mt <- attr(mf, "terms")@\\
\mbox{}\verb@    names(betas) <- colnames(mm)@\\
\mbox{}\verb@    names(referencef0) <- 0:N@\\
\mbox{}\verb@    rownames(vc) <- colnames(vc) <- c(names(betas), names(referencef0))@\\
\mbox{}\verb@    res <- list(coefficients = betas, f0=referencef0, vcov = vc, mu0=mu0, niter = iter, @\\
\mbox{}\verb@                loglik=llik, link = link, call = mc, terms = mt,@\\
\mbox{}\verb@                xlevels = .getXlevels(mt, mf),@\\
\mbox{}\verb@                data_object=data_object)@\\
\mbox{}\verb@    class(res) <- "spglm"@\\
\mbox{}\verb@    res@\\
\mbox{}\verb@@\\
\mbox{}\verb@}@\\
\mbox{}\verb@@{\NWsep}
\end{list}
\vspace{-1.5ex}
\footnotesize
\begin{list}{}{\setlength{\itemsep}{-\parsep}\setlength{\itemindent}{-\leftmargin}}
\item \NWtxtFileDefBy\ \NWlink{nuweb1}{1}\NWlink{nuweb3}{, 3}\NWlink{nuweb4}{, 4}\NWlink{nuweb5}{, 5}\NWlink{nuweb6}{, 6}\NWlink{nuweb?}{, ?}.

@@

\begin{flushleft} \small\label{scrap3}\raggedright\small
\NWtarget{nuweb3}{} \verb@"../R/SPGLM.R"@\nobreak\ {\footnotesize {3}}$\equiv$
\vspace{-1ex}
\begin{list}{}{} \item
\mbox{}\verb@@\\
\mbox{}\verb@#' @{\tt @}\verb@export@\\
\mbox{}\verb@#' @{\tt @}\verb@importFrom stats printCoefmat@\\
\mbox{}\verb@print.spglm <- function(x, digits = max(3L, getOption("digits") - 3L),...){@\\
\mbox{}\verb@  # based on print.lm, summary.lm, and print.summary.lm@\\
\mbox{}\verb@  cat("\nA semi-parametric generalized linear regression model fit\n")@\\
\mbox{}\verb@  cat("\nCall:\n", paste(deparse(x$call), sep = "\n", collapse = "\n"),@\\
\mbox{}\verb@        "\n\n", sep = "")@\\
\mbox{}\verb@  if (length(x$coefficients)) {@\\
\mbox{}\verb@    beta <- x$coefficients@\\
\mbox{}\verb@    p <- length(beta)@\\
\mbox{}\verb@    SEbeta <- sqrt(diag(x$vcov[1:p, 1:p]))@\\
\mbox{}\verb@    z <- beta / SEbeta@\\
\mbox{}\verb@    pval <- 2 * stats::pnorm(abs(z), lower.tail=FALSE)@\\
\mbox{}\verb@    coefmat <-  cbind(Estimate = beta, `Std. Error` = SEbeta, @\\
\mbox{}\verb@                      `z value` = z, `Pr(>|z|)` = pval)@\\
\mbox{}\verb@    cat("Coefficients:\n")@\\
\mbox{}\verb@    printCoefmat(coefmat, digits = digits, na.print = "NA", ...)@\\
\mbox{}\verb@    }@\\
\mbox{}\verb@    else cat("No coefficients\n")@\\
\mbox{}\verb@@\\
\mbox{}\verb@    if (length(x$f0)){@\\
\mbox{}\verb@        cat("\n Baseline probabilities (q0):\n")        @\\
\mbox{}\verb@        q0 <- x$f0@\\
\mbox{}\verb@         print.default(format(q0, digits = digits),@\\
\mbox{}\verb@            print.gap = 2, quote = FALSE)@\\
\mbox{}\verb@    }@\\
\mbox{}\verb@    else cat("No baseline joint probabilities\n")@\\
\mbox{}\verb@@\\
\mbox{}\verb@   cat("\n Log-likelihood: ", format(x$loglik, digits=digits), "\n")@\\
\mbox{}\verb@   invisible(x)@\\
\mbox{}\verb@}@\\
\mbox{}\verb@@{\NWsep}
\end{list}
\vspace{-1.5ex}
\footnotesize
\begin{list}{}{\setlength{\itemsep}{-\parsep}\setlength{\itemindent}{-\leftmargin}}
\item \NWtxtFileDefBy\ \NWlink{nuweb1}{1}\NWlink{nuweb3}{, 3}\NWlink{nuweb4}{, 4}\NWlink{nuweb5}{, 5}\NWlink{nuweb6}{, 6}\NWlink{nuweb?}{, ?}.

@@

\begin{flushleft} \small\label{scrap4}\raggedright\small
\NWtarget{nuweb4}{} \verb@"../R/SPGLM.R"@\nobreak\ {\footnotesize {4}}$\equiv$
\vspace{-1ex}
\begin{list}{}{} \item
\mbox{}\verb@@\\
\mbox{}\verb@#' Extracting components of fitted `spglm` object@\\
\mbox{}\verb@#'@\\
\mbox{}\verb@#' @{\tt @}\verb@param object fitted model of class \code{spglm}@\\
\mbox{}\verb@#' @{\tt @}\verb@param beta logical, whether the regression parameter estimates / variances should be returned@\\
\mbox{}\verb@#' @{\tt @}\verb@param f0 logical, whether the backbone density estimates / variances should be returned@\\
\mbox{}\verb@#' @{\tt @}\verb@param ... not used, present fo consistency with generics@\\
\mbox{}\verb@#' @{\tt @}\verb@importFrom stats coef@\\
\mbox{}\verb@#' @{\tt @}\verb@export@\\
\mbox{}\verb@@\\
\mbox{}\verb@coef.spglm <- function(object, beta=TRUE, f0=FALSE, ...){@\\
\mbox{}\verb@  res <- NULL@\\
\mbox{}\verb@  if (beta) res <- c(res, object$coefficients)@\\
\mbox{}\verb@  if (f0) res <- c(res, object$f0)@\\
\mbox{}\verb@  res@\\
\mbox{}\verb@}@\\
\mbox{}\verb@@\\
\mbox{}\verb@#' @{\tt @}\verb@rdname coef.spglm@\\
\mbox{}\verb@#'@\\
\mbox{}\verb@#' @{\tt @}\verb@importFrom stats vcov@\\
\mbox{}\verb@#' @{\tt @}\verb@export@\\
\mbox{}\verb@vcov.spglm <- function(object, beta=TRUE, f0=FALSE, ...){@\\
\mbox{}\verb@  p <- length(object$coefficients)@\\
\mbox{}\verb@  m <- nrow(object$vcov)@\\
\mbox{}\verb@  @\\
\mbox{}\verb@  idx <- NULL@\\
\mbox{}\verb@  if (beta) idx <- c(idx, 1:p)@\\
\mbox{}\verb@  if (f0) idx <- c(idx, (p+1):m)@\\
\mbox{}\verb@  @\\
\mbox{}\verb@  vc <- object$vcov[idx,idx]@\\
\mbox{}\verb@  vc@\\
\mbox{}\verb@}@\\
\mbox{}\verb@@\\
\mbox{}\verb@#' @{\tt @}\verb@rdname coef.spglm@\\
\mbox{}\verb@#'@\\
\mbox{}\verb@#' @{\tt @}\verb@importFrom stats logLik@\\
\mbox{}\verb@#' @{\tt @}\verb@export@\\
\mbox{}\verb@logLik.spglm <- function(object, ...){@\\
\mbox{}\verb@  object$loglik@\\
\mbox{}\verb@}@\\
\mbox{}\verb@                              @\\
\mbox{}\verb@@{\NWsep}
\end{list}
\vspace{-1.5ex}
\footnotesize
\begin{list}{}{\setlength{\itemsep}{-\parsep}\setlength{\itemindent}{-\leftmargin}}
\item \NWtxtFileDefBy\ \NWlink{nuweb1}{1}\NWlink{nuweb3}{, 3}\NWlink{nuweb4}{, 4}\NWlink{nuweb5}{, 5}\NWlink{nuweb6}{, 6}\NWlink{nuweb?}{, ?}.

@@

\item \NWtxtFileDefBy\ \NWlink{nuweb1}{1}\NWlink{nuweb3}{, 3}\NWlink{nuweb4}{, 4}\NWlink{nuweb5}{, 5}\NWlink{nuweb6}{, 6}\NWlink{nuweb?}{, ?}.

@@

\begin{flushleft} \small\label{scrap6}\raggedright\small
\NWtarget{nuweb6}{} \verb@"../R/SPGLM.R"@\nobreak\ {\footnotesize {6}}$\equiv$
\vspace{-1ex}
\begin{list}{}{} \item
\mbox{}\verb@@\\
\mbox{}\verb@#' @{\tt @}\verb@keywords internal@\\
\mbox{}\verb@#' @{\tt @}\verb@importFrom stats dhyper@\\
\mbox{}\verb@spglm_lp <- function(beta, data_object){@\\
\mbox{}\verb@  eta <- c(data_object$model_matrix %*% beta + data_object$offset)@\\
\mbox{}\verb@  eta@\\
\mbox{}\verb@}@\\
\mbox{}\verb@@\\
\mbox{}\verb@spglm_pred_mean <- function(beta, data_object, link){@\\
\mbox{}\verb@  eta <- c(data_object$model_matrix %*% beta + data_object$offset)@\\
\mbox{}\verb@  mu <- link$linkinv(eta)@\\
\mbox{}\verb@  mu@\\
\mbox{}\verb@}@\\
\mbox{}\verb@@\\
\mbox{}\verb@spglm_tilt <- function(beta, f0, data_object, link){@\\
\mbox{}\verb@@\\
\mbox{}\verb@    mu <- spglm_pred_mean(beta=beta, data_object=data_object, link=link)@\\
\mbox{}\verb@    N <- data_object$maxN@\\
\mbox{}\verb@    nobs <- nrow(data_object$model_matrix)@\\
\mbox{}\verb@    spt <- data_object$spt@\\
\mbox{}\verb@    @\\
\mbox{}\verb@    # ySptIndex is only used to calculate the log-likelihood, which we will not be using@\\
\mbox{}\verb@    th <- getTheta(spt=spt/N, f0=f0[spt+1], mu=mu, weights=data_object$weights, ySptIndex=rep(1, nobs),@\\
\mbox{}\verb@                   thetaStart=NULL, thetaControl=theta.control())@\\
\mbox{}\verb@    th$theta@\\
\mbox{}\verb@}@\\
\mbox{}\verb@@\\
\mbox{}\verb@spglm_probs <- function(beta, f0, data_object, link){@\\
\mbox{}\verb@@\\
\mbox{}\verb@    mu <- spglm_pred_mean(beta=beta, data_object=data_object, link=link)@\\
\mbox{}\verb@    N <- data_object$maxN@\\
\mbox{}\verb@    nobs <- nrow(data_object$model_matrix)@\\
\mbox{}\verb@    spt <- data_object$spt@\\
\mbox{}\verb@   @\\
\mbox{}\verb@    # ySptIndex is only used to calculate the log-likelihood, which we will not be using@\\
\mbox{}\verb@    th <- getTheta(spt=spt/N, f0=f0[spt+1], mu=mu, weights=data_object$weights, ySptIndex=rep(1, nobs),@\\
\mbox{}\verb@                   thetaStart=NULL, thetaControl=theta.control())@\\
\mbox{}\verb@                   @\\
\mbox{}\verb@    hp <- sapply(0:N, function(t)dhyper(x=data_object$resp[,1], m=data_object$n, n=N-data_object$n, k=t))  @\\
\mbox{}\verb@    @\\
\mbox{}\verb@    # fill in 0's for values with no support@\\
\mbox{}\verb@    fTilt <- matrix(0, ncol = nobs, nrow = N+1)@\\
\mbox{}\verb@    fTilt[spt+1,] <- th$fTilt@\\
\mbox{}\verb@    #probs <- rowSums(t(th$fTilt) * hp)@\\
\mbox{}\verb@    probs <- rowSums(t(fTilt) * hp)@\\
\mbox{}\verb@    probs@\\
\mbox{}\verb@}@\\
\mbox{}\verb@@\\
\mbox{}\verb@spglm_loglik <- function(beta, f0, data_object, link){@\\
\mbox{}\verb@  @\\
\mbox{}\verb@    probs <- spglm_probs(beta, f0, data_object, link)@\\
\mbox{}\verb@    llik <- log(probs) %*% data_object$weights@\\
\mbox{}\verb@    c(llik)@\\
\mbox{}\verb@}@\\
\mbox{}\verb@@{\NWsep}
\end{list}
\vspace{-1.5ex}
\footnotesize
\begin{list}{}{\setlength{\itemsep}{-\parsep}\setlength{\itemindent}{-\leftmargin}}
\item \NWtxtFileDefBy\ \NWlink{nuweb1}{1}\NWlink{nuweb3}{, 3}\NWlink{nuweb4}{, 4}\NWlink{nuweb5}{, 5}\NWlink{nuweb6}{, 6}\NWlink{nuweb?}{, ?}.

@@

\begin{flushleft} \small\label{scrap9}\raggedright\small
\NWtarget{nuweb9a}{} $\langle\,${\itshape E-step}\nobreak\ {\footnotesize {9a}}$\,\rangle\equiv$
\vspace{-1ex}
\begin{list}{}{} \item
\mbox{}\verb@@\\
\mbox{}\verb@  # convert fTiltMatrix to long vector, watching out for potentially different support@\\
\mbox{}\verb@  y_idx <- match(Ycomb[,"y"], 0:N)@\\
\mbox{}\verb@  fTilt2 <- ifelse(!is.na(y_idx), fTiltMatrix[cbind(Ycomb[,"i"], y_idx)], 0)@\\
\mbox{}\verb@  @\\
\mbox{}\verb@  # numerator of weights@\\
\mbox{}\verb@  pp_num <- choose(n=Ycomb[,"y"], k=Ycomb[,"resp"]) * @\\
\mbox{}\verb@           choose(n=N-Ycomb[,"y"], k=Ycomb[,"nonresp"]) * @\\
\mbox{}\verb@           fTilt2@\\
\mbox{}\verb@  # denominator @\\
\mbox{}\verb@  pp_denom <- tapply(pp_num, list(i=Ycomb[,"i"]), sum, simplify=TRUE)@\\
\mbox{}\verb@  pp <- c(pp_num / pp_denom[Ycomb[,"i"]])@\\
\mbox{}\verb@  if (!is.null(weights)) pp <- weights2 * pp@\\
\mbox{}\verb@@{\NWsep}
\end{list}
\vspace{-1.5ex}
\footnotesize
\begin{list}{}{\setlength{\itemsep}{-\parsep}\setlength{\itemindent}{-\leftmargin}}
\item \NWtxtMacroRefIn\ \NWlink{nuweb7}{7}.

>>>>

\begin{flushleft} \small\label{scrap1}\raggedright\small
\NWtarget{nuweb1}{} \verb@"../R/SPGLM.R"@\nobreak\ {\footnotesize {1}}$\equiv$
\vspace{-1ex}
\begin{list}{}{} \item
\mbox{}\verb@@\\
\mbox{}\verb@#' Fit semi-parametric GLM@\\
\mbox{}\verb@#'@\\
\mbox{}\verb@#'@{\tt @}\verb@rdname spglm@\\
\mbox{}\verb@#'@{\tt @}\verb@param formula a one-sided formula of the form \code{cbind(r, s) ~ predictors} where \code{r} and \code{s} give the number of responses and non-responses within each cluster, respectively (so the cluster size is \code{r+s}), and \code{predictors} describes the covariates.@\\
\mbox{}\verb@#'@{\tt @}\verb@param data  an optional matrix or data frame containing the variables in the formula \code{formula}. By default the variables are taken from \code{environment(formula).}@\\
\mbox{}\verb@#'@{\tt @}\verb@param subset  an optional vector specifying a subset of observations to be used.@\\
\mbox{}\verb@#'@{\tt @}\verb@param weights an optional vector specifying observation weights.@\\
\mbox{}\verb@#'@{\tt @}\verb@param offset  an optional vector specifying an offset term (predictor with a fixed coefficient of 1).@\\
\mbox{}\verb@#'@{\tt @}\verb@param link      a link function for the mean.@\\
\mbox{}\verb@#'@{\tt @}\verb@param mu0       an optional numeric value constraining the mean of the baseline distribution@\\
\mbox{}\verb@#'@{\tt @}\verb@param control a list with parameters controlling the algorithm.@\\
\mbox{}\verb@#'@{\tt @}\verb@return an object of class \code{spglm} with the fitted model.@\\
\mbox{}\verb@#'@{\tt @}\verb@export@\\
\mbox{}\verb@#' @{\tt @}\verb@importFrom stats terms model.matrix model.frame model.offset model.response model.weights@\\
\mbox{}\verb@@\\
\mbox{}\verb@spglm <- function(formula, data, subset, weights, offset, link="logit", mu0=NULL, @\\
\mbox{}\verb@                  control=list(eps=0.001, maxit=100)){@\\
\mbox{}\verb@@\\
\mbox{}\verb@    @\hbox{$\langle\,${\itshape Create model matrix from formula and data}\nobreak\ {\footnotesize \NWlink{nuweb2}{2}}$\,\rangle$}\verb@@\\
\mbox{}\verb@    @\\
\mbox{}\verb@    data_object <- list(model_matrix=mm, resp=Y, n=rowSums(Y), weights=weights, offset=offset, @\\
\mbox{}\verb@                        maxN=N, spt=0:N)@\\
\mbox{}\verb@    @\\
\mbox{}\verb@    @\hbox{$\langle\,${\itshape Fit model}\nobreak\ {\footnotesize \NWlink{nuweb7}{7}}$\,\rangle$}\verb@@\\
\mbox{}\verb@@\\
\mbox{}\verb@    mt <- attr(mf, "terms")@\\
\mbox{}\verb@    names(betas) <- colnames(mm)@\\
\mbox{}\verb@    names(referencef0) <- 0:N@\\
\mbox{}\verb@    rownames(vc) <- colnames(vc) <- c(names(betas), names(referencef0))@\\
\mbox{}\verb@    res <- list(coefficients = betas, f0=referencef0, vcov = vc, mu0=mu0, niter = iter, @\\
\mbox{}\verb@                loglik=llik, link = link, call = mc, terms = mt,@\\
\mbox{}\verb@                xlevels = .getXlevels(mt, mf),@\\
\mbox{}\verb@                data_object=data_object)@\\
\mbox{}\verb@    class(res) <- "spglm"@\\
\mbox{}\verb@    res@\\
\mbox{}\verb@@\\
\mbox{}\verb@}@\\
\mbox{}\verb@@{\NWsep}
\end{list}
\vspace{-1.5ex}
\footnotesize
\begin{list}{}{\setlength{\itemsep}{-\parsep}\setlength{\itemindent}{-\leftmargin}}
\item \NWtxtFileDefBy\ \NWlink{nuweb1}{1}\NWlink{nuweb3}{, 3}\NWlink{nuweb4}{, 4}\NWlink{nuweb5}{, 5}\NWlink{nuweb6}{, 6}\NWlink{nuweb12}{, 12}.

@@

\begin{flushleft} \small\label{scrap3}\raggedright\small
\NWtarget{nuweb3}{} \verb@"../R/SPGLM.R"@\nobreak\ {\footnotesize {3}}$\equiv$
\vspace{-1ex}
\begin{list}{}{} \item
\mbox{}\verb@@\\
\mbox{}\verb@#' @{\tt @}\verb@export@\\
\mbox{}\verb@#' @{\tt @}\verb@importFrom stats printCoefmat@\\
\mbox{}\verb@print.spglm <- function(x, digits = max(3L, getOption("digits") - 3L),...){@\\
\mbox{}\verb@  # based on print.lm, summary.lm, and print.summary.lm@\\
\mbox{}\verb@  cat("\nA semi-parametric generalized linear regression model fit\n")@\\
\mbox{}\verb@  cat("\nCall:\n", paste(deparse(x$call), sep = "\n", collapse = "\n"),@\\
\mbox{}\verb@        "\n\n", sep = "")@\\
\mbox{}\verb@  if (length(x$coefficients)) {@\\
\mbox{}\verb@    beta <- x$coefficients@\\
\mbox{}\verb@    p <- length(beta)@\\
\mbox{}\verb@    SEbeta <- sqrt(diag(x$vcov[1:p, 1:p]))@\\
\mbox{}\verb@    z <- beta / SEbeta@\\
\mbox{}\verb@    pval <- 2 * stats::pnorm(abs(z), lower.tail=FALSE)@\\
\mbox{}\verb@    coefmat <-  cbind(Estimate = beta, `Std. Error` = SEbeta, @\\
\mbox{}\verb@                      `z value` = z, `Pr(>|z|)` = pval)@\\
\mbox{}\verb@    cat("Coefficients:\n")@\\
\mbox{}\verb@    printCoefmat(coefmat, digits = digits, na.print = "NA", ...)@\\
\mbox{}\verb@    }@\\
\mbox{}\verb@    else cat("No coefficients\n")@\\
\mbox{}\verb@@\\
\mbox{}\verb@    if (length(x$f0)){@\\
\mbox{}\verb@        cat("\n Baseline probabilities (q0):\n")        @\\
\mbox{}\verb@        q0 <- x$f0@\\
\mbox{}\verb@         print.default(format(q0, digits = digits),@\\
\mbox{}\verb@            print.gap = 2, quote = FALSE)@\\
\mbox{}\verb@    }@\\
\mbox{}\verb@    else cat("No baseline joint probabilities\n")@\\
\mbox{}\verb@@\\
\mbox{}\verb@   cat("\n Log-likelihood: ", format(x$loglik, digits=digits), "\n")@\\
\mbox{}\verb@   invisible(x)@\\
\mbox{}\verb@}@\\
\mbox{}\verb@@{\NWsep}
\end{list}
\vspace{-1.5ex}
\footnotesize
\begin{list}{}{\setlength{\itemsep}{-\parsep}\setlength{\itemindent}{-\leftmargin}}
\item \NWtxtFileDefBy\ \NWlink{nuweb1}{1}\NWlink{nuweb3}{, 3}\NWlink{nuweb4}{, 4}\NWlink{nuweb5}{, 5}\NWlink{nuweb6}{, 6}\NWlink{nuweb12}{, 12}.

@@

\begin{flushleft} \small\label{scrap4}\raggedright\small
\NWtarget{nuweb4}{} \verb@"../R/SPGLM.R"@\nobreak\ {\footnotesize {4}}$\equiv$
\vspace{-1ex}
\begin{list}{}{} \item
\mbox{}\verb@@\\
\mbox{}\verb@#' Extracting components of fitted `spglm` object@\\
\mbox{}\verb@#'@\\
\mbox{}\verb@#' @{\tt @}\verb@param object fitted model of class \code{spglm}@\\
\mbox{}\verb@#' @{\tt @}\verb@param beta logical, whether the regression parameter estimates / variances should be returned@\\
\mbox{}\verb@#' @{\tt @}\verb@param f0 logical, whether the backbone density estimates / variances should be returned@\\
\mbox{}\verb@#' @{\tt @}\verb@param ... not used, present fo consistency with generics@\\
\mbox{}\verb@#' @{\tt @}\verb@importFrom stats coef@\\
\mbox{}\verb@#' @{\tt @}\verb@export@\\
\mbox{}\verb@@\\
\mbox{}\verb@coef.spglm <- function(object, beta=TRUE, f0=FALSE, ...){@\\
\mbox{}\verb@  res <- NULL@\\
\mbox{}\verb@  if (beta) res <- c(res, object$coefficients)@\\
\mbox{}\verb@  if (f0) res <- c(res, object$f0)@\\
\mbox{}\verb@  res@\\
\mbox{}\verb@}@\\
\mbox{}\verb@@\\
\mbox{}\verb@#' @{\tt @}\verb@rdname coef.spglm@\\
\mbox{}\verb@#'@\\
\mbox{}\verb@#' @{\tt @}\verb@importFrom stats vcov@\\
\mbox{}\verb@#' @{\tt @}\verb@export@\\
\mbox{}\verb@vcov.spglm <- function(object, beta=TRUE, f0=FALSE, ...){@\\
\mbox{}\verb@  p <- length(object$coefficients)@\\
\mbox{}\verb@  m <- nrow(object$vcov)@\\
\mbox{}\verb@  @\\
\mbox{}\verb@  idx <- NULL@\\
\mbox{}\verb@  if (beta) idx <- c(idx, 1:p)@\\
\mbox{}\verb@  if (f0) idx <- c(idx, (p+1):m)@\\
\mbox{}\verb@  @\\
\mbox{}\verb@  vc <- object$vcov[idx,idx]@\\
\mbox{}\verb@  vc@\\
\mbox{}\verb@}@\\
\mbox{}\verb@@\\
\mbox{}\verb@#' @{\tt @}\verb@rdname coef.spglm@\\
\mbox{}\verb@#'@\\
\mbox{}\verb@#' @{\tt @}\verb@importFrom stats logLik@\\
\mbox{}\verb@#' @{\tt @}\verb@export@\\
\mbox{}\verb@logLik.spglm <- function(object, ...){@\\
\mbox{}\verb@  object$loglik@\\
\mbox{}\verb@}@\\
\mbox{}\verb@                              @\\
\mbox{}\verb@@{\NWsep}
\end{list}
\vspace{-1.5ex}
\footnotesize
\begin{list}{}{\setlength{\itemsep}{-\parsep}\setlength{\itemindent}{-\leftmargin}}
\item \NWtxtFileDefBy\ \NWlink{nuweb1}{1}\NWlink{nuweb3}{, 3}\NWlink{nuweb4}{, 4}\NWlink{nuweb5}{, 5}\NWlink{nuweb6}{, 6}\NWlink{nuweb12}{, 12}.

@@

\item \NWtxtFileDefBy\ \NWlink{nuweb1}{1}\NWlink{nuweb3}{, 3}\NWlink{nuweb4}{, 4}\NWlink{nuweb5}{, 5}\NWlink{nuweb6}{, 6}\NWlink{nuweb12}{, 12}.

@@

\begin{flushleft} \small\label{scrap6}\raggedright\small
\NWtarget{nuweb6}{} \verb@"../R/SPGLM.R"@\nobreak\ {\footnotesize {6}}$\equiv$
\vspace{-1ex}
\begin{list}{}{} \item
\mbox{}\verb@@\\
\mbox{}\verb@#' @{\tt @}\verb@keywords internal@\\
\mbox{}\verb@#' @{\tt @}\verb@importFrom stats dhyper@\\
\mbox{}\verb@spglm_lp <- function(beta, data_object){@\\
\mbox{}\verb@  eta <- c(data_object$model_matrix %*% beta + data_object$offset)@\\
\mbox{}\verb@  eta@\\
\mbox{}\verb@}@\\
\mbox{}\verb@@\\
\mbox{}\verb@spglm_pred_mean <- function(beta, data_object, link){@\\
\mbox{}\verb@  eta <- c(data_object$model_matrix %*% beta + data_object$offset)@\\
\mbox{}\verb@  mu <- link$linkinv(eta)@\\
\mbox{}\verb@  mu@\\
\mbox{}\verb@}@\\
\mbox{}\verb@@\\
\mbox{}\verb@spglm_tilt <- function(beta, f0, data_object, link){@\\
\mbox{}\verb@@\\
\mbox{}\verb@    mu <- spglm_pred_mean(beta=beta, data_object=data_object, link=link)@\\
\mbox{}\verb@    N <- data_object$maxN@\\
\mbox{}\verb@    nobs <- nrow(data_object$model_matrix)@\\
\mbox{}\verb@    spt <- data_object$spt@\\
\mbox{}\verb@    @\\
\mbox{}\verb@    # ySptIndex is only used to calculate the log-likelihood, which we will not be using@\\
\mbox{}\verb@    th <- getTheta(spt=spt/N, f0=f0[spt+1], mu=mu, weights=data_object$weights, ySptIndex=rep(1, nobs),@\\
\mbox{}\verb@                   thetaStart=NULL, thetaControl=theta.control())@\\
\mbox{}\verb@    th$theta@\\
\mbox{}\verb@}@\\
\mbox{}\verb@@\\
\mbox{}\verb@spglm_probs <- function(beta, f0, data_object, link){@\\
\mbox{}\verb@@\\
\mbox{}\verb@    mu <- spglm_pred_mean(beta=beta, data_object=data_object, link=link)@\\
\mbox{}\verb@    N <- data_object$maxN@\\
\mbox{}\verb@    nobs <- nrow(data_object$model_matrix)@\\
\mbox{}\verb@    spt <- data_object$spt@\\
\mbox{}\verb@   @\\
\mbox{}\verb@    # ySptIndex is only used to calculate the log-likelihood, which we will not be using@\\
\mbox{}\verb@    th <- getTheta(spt=spt/N, f0=f0[spt+1], mu=mu, weights=data_object$weights, ySptIndex=rep(1, nobs),@\\
\mbox{}\verb@                   thetaStart=NULL, thetaControl=theta.control())@\\
\mbox{}\verb@                   @\\
\mbox{}\verb@    if (is.null(data_object$hyper_probs)){                   @\\
\mbox{}\verb@      hp <- sapply(0:N, function(t)dhyper(x=data_object$resp[,1], m=data_object$n, @\\
\mbox{}\verb@                   n=N-data_object$n, k=t))@\\
\mbox{}\verb@    } else {@\\
\mbox{}\verb@      hp <- data_object$hyper_probs@\\
\mbox{}\verb@    }@\\
\mbox{}\verb@    @\\
\mbox{}\verb@    # fill in 0's for values with no support@\\
\mbox{}\verb@    fTilt <- matrix(0, ncol = nobs, nrow = N+1)@\\
\mbox{}\verb@    fTilt[spt+1,] <- th$fTilt@\\
\mbox{}\verb@    #probs <- rowSums(t(th$fTilt) * hp)@\\
\mbox{}\verb@    probs <- rowSums(t(fTilt) * hp)@\\
\mbox{}\verb@    probs@\\
\mbox{}\verb@}@\\
\mbox{}\verb@@\\
\mbox{}\verb@spglm_loglik <- function(beta, f0, data_object, link){@\\
\mbox{}\verb@  @\\
\mbox{}\verb@    probs <- spglm_probs(beta, f0, data_object, link)@\\
\mbox{}\verb@    llik <- log(probs) %*% data_object$weights@\\
\mbox{}\verb@    c(llik)@\\
\mbox{}\verb@}@\\
\mbox{}\verb@@{\NWsep}
\end{list}
\vspace{-1.5ex}
\footnotesize
\begin{list}{}{\setlength{\itemsep}{-\parsep}\setlength{\itemindent}{-\leftmargin}}
\item \NWtxtFileDefBy\ \NWlink{nuweb1}{1}\NWlink{nuweb3}{, 3}\NWlink{nuweb4}{, 4}\NWlink{nuweb5}{, 5}\NWlink{nuweb6}{, 6}\NWlink{nuweb12}{, 12}.

@@

\begin{flushleft} \small\label{scrap9}\raggedright\small
\NWtarget{nuweb9}{} $\langle\,${\itshape E-step}\nobreak\ {\footnotesize {9}}$\,\rangle\equiv$
\vspace{-1ex}
\begin{list}{}{} \item
\mbox{}\verb@@\\
\mbox{}\verb@  # convert fTiltMatrix to long vector, watching out for potentially different support@\\
\mbox{}\verb@  y_idx <- match(Ycomb[,"y"], 0:N)@\\
\mbox{}\verb@  fTilt2 <- ifelse(!is.na(y_idx), fTiltMatrix[cbind(Ycomb[,"i"], y_idx)], 0)@\\
\mbox{}\verb@  @\\
\mbox{}\verb@  # numerator of weights@\\
\mbox{}\verb@  pp_num <- choose(n=Ycomb[,"y"], k=Ycomb[,"resp"]) * @\\
\mbox{}\verb@           choose(n=N-Ycomb[,"y"], k=Ycomb[,"nonresp"]) * @\\
\mbox{}\verb@           fTilt2@\\
\mbox{}\verb@  # denominator @\\
\mbox{}\verb@  pp_denom <- tapply(pp_num, list(i=Ycomb[,"i"]), sum, simplify=TRUE)@\\
\mbox{}\verb@  pp <- c(pp_num / pp_denom[Ycomb[,"i"]])@\\
\mbox{}\verb@  if (!is.null(weights)) pp <- weights2 * pp@\\
\mbox{}\verb@@{\NWsep}
\end{list}
\vspace{-1.5ex}
\footnotesize
\begin{list}{}{\setlength{\itemsep}{-\parsep}\setlength{\itemindent}{-\leftmargin}}
\item \NWtxtMacroRefIn\ \NWlink{nuweb7}{7}.
